Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-24 paper.tex
xavier acknowl.

\para{Acknowledgements.}
We thank Jasmin Blanchette and Massin Guerdi for their valuable comments on drafts of this paper.
\jcom{TODO Xavier funding.}

>>>>

\para{Acknowledgements.}
We thank Jasmin Blanchette and Massin Guerdi for their valuable comments on drafts of this paper.
Généreux's research was co-funded by the European Union (ERC, Nekoka, 101083038) and by the Fonds de recherche du Québec, 330205. Views and opinions expressed are however those of the authors only and do not necessarily reflect those of the European Union or the European Research Council. Neither the European Union nor the granting authority can be held responsible for them.
